|

### 2022-12-03 paper_comparison/paper_comparison/paper_comparison.Rmd
Use power 4 for the RESET test

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = mod$test(tmp_dat)$p_value,
                            RESET_p_value = mod$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = POLY_MODEL$test(mutate(tmp_dat, z = poly_model()$gen(n, computed = select(tmp_dat, x))$z))$p_value,
                            RESET_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            BP_p_value = mod$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(6, "Safe"))[2:6]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(6, "Safe"))[2:6]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

>>>>

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = mod$test(tmp_dat)$p_value,
                            RESET3_p_value = mod$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            RESET4_p_value = mod$test(tmp_dat, test = "RESET", power = 2:4, power_type = "fitted")$p_value,
                            RESET5_p_value = mod$test(tmp_dat, test = "RESET", power = 2:5, power_type = "fitted")$p_value,
                            RESET6_p_value = mod$test(tmp_dat, test = "RESET", power = 2:6, power_type = "fitted")$p_value,
                            RESET7_p_value = mod$test(tmp_dat, test = "RESET", power = 2:7, power_type = "fitted")$p_value,
                            RESET8_p_value = mod$test(tmp_dat, test = "RESET", power = 2:8, power_type = "fitted")$p_value,
                            RESET9_p_value = mod$test(tmp_dat, test = "RESET", power = 2:9, power_type = "fitted")$p_value,
                            RESET10_p_value = mod$test(tmp_dat, test = "RESET", power = 2:10, power_type = "fitted")$p_value,
                            BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = POLY_MODEL$test(mutate(tmp_dat, z = poly_model()$gen(n, computed = select(tmp_dat, x))$z))$p_value,
                            RESET3_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            RESET4_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:4, power_type = "fitted")$p_value,
                            RESET5_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:5, power_type = "fitted")$p_value,
                            RESET6_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:6, power_type = "fitted")$p_value,
                            RESET7_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:7, power_type = "fitted")$p_value,
                            RESET8_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:8, power_type = "fitted")$p_value,
                            RESET9_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:9, power_type = "fitted")$p_value,
                            RESET10_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:10, power_type = "fitted")$p_value,
                            BP_p_value = mod$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(6, "Safe"))[2:6]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

```{r eval = FALSE}

# For checking RESET test
plotly::ggplotly(ggplot() +
geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                # select(-(RESET4_p_value:RESET10_p_value)) %>%
                pivot_longer(F_p_value:RESET10_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = factor(name, levels = c(paste0("RESET", 3:10, " test"), "F test"))), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  scale_color_brewer("YlGnBu") +
  labs(col = "") +
  xlab("Log of effect size") +
  ylab("Power") +
  ggtitle("Power of the RESET test under different powers of the fitted values"))
```

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(6, "Safe"))[2:6]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")
